% $Id$
% This article, originally published in TUGboat 32:1 (2011), is now
% released to the public domain by the authors. PDF for the TUGboat
% publication: https://tug.org/TUGboat/tb32-1/tb100walden.pdf.
% 
\documentclass[final]{ltugboat}
\usepackage{url}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{microtype}
\interlinepenalty = -250

\def\URL{\acro{URL}}
\def\TPJ{\textsl{The Prac\TeX\ Journal\/}}
\def\LB#1{\smallskip\noindent\textbf{#1.}~}

\title{\TUB\ online}
\author{Karl Berry and David Walden}
\EDITORnoaddress
\netaddress{http://tug.org/TUGboat/Contents}

\begin{document}
\maketitle

\section{Introduction}

\TUB\ has traditionally been, and remains, a print journal.  Its history
was described and profusely illustrated in Barbara Beeton's 2006 paper
(``How to Create a \TeX\ Journal: A Personal Journey'', \TUB\ 28:1,
2007, pp.\ 29--49,
\url{http://tug.org/TUGboat/tb28-1/tb88beet-keynote.pdf}).

Since the web came into being, \TUB\ has also existed online.  This
article sketches the evolution of the online version of \TUB.


\section{First steps}\label{sec:prior}

\TUB\ has been part of the \tug\ web site since the web site's
beginning.  To a large extent, the original pages remain, with the basic
description of the journal, editor's wish list, information for authors,
and so on.

It was apparent from the outset that it would be useful to publish back
issues on the web.  Mimi Burbank began the process of scanning paper
copies.  In a few cases articles were reprocessed, or \DVI\ converted to
\PDF, but in the main, sources, figures, and\slash or fonts were lacking, so
no systematic reprocessing could be attempted.  Scanning to \PDF\ was
the only viable approach.

As the work proceeded, Mimi created table of contents files in \HTML\ by
hand.  The scanning took so much more time than writing the \HTML, and
was proceeding so slowly, there was no need to think about any tools.

As the years passed, additional volunteers came forward.  In particular,
Brooks Moses (with the support of his department at Stanford) ended up
doing the bulk of the scanning.  Robin Laakso in the \tug\ office also
made significant contributions.  Most of the issues were scanned by
2006, though the process was not completely finished until 2009, so the
scanning overlapped with the other work we describe below.  (Even now,
additional work remains\Dash some of the early issues were scanned at
150\,dpi, some pages are crooked, a few pages are missing, etc.)

Once enough back issues had become available, the question arose of how
best to make the material accessible on the web.  Our attempts to answer
that question are described in the rest of this article.


\section{Two steps toward automating generation of \TUB\ tables of contents}

\subsection{\TPJ}
\label{sec:tpj}

In 2004, \tug, at the suggestion of Lance Carnes, sponsored a \TeX\
conference explicitly focused on practical use of \TeX.  Near the end of
the conference, Tim Null and Robin Laakso discussed developing a section
of the \tug\ web site that would contain introductory material on \TeX\
organized by category.  In an exchange of emails between Tim Null and
Karl Berry after the conference, Tim came up with the alternative idea
of an online journal.  Lance Carnes became the editor of that journal,
and other people volunteered or were recruited to join the new journal's
editorial board.

The Editorial Board's planning discussions naturally were centered on
issues such as the target audience, look and feel, and frequency and
schedule.  Meanwhile, Karl hand-crafted \HTML\ for a prototype web site
for the new journal, and other members of the editorial board made many
comments on it.  We then embarked on a collaboration to build a
production program to generate a web site similar to the prototype.  The
initial issue of \TPJ\ was published (posted at
\url{http://tug.org/pracjourn}, which remains the journal's home) on
January~15, 2005.  This web site includes a table of contents for each
issue with links to the \PDF{}s of the papers, and author, title, and
\BibTeX\ lists covering all issues.

The relevance of the \textsl{Prac\TeX\ Journal\/} effort to \TUB\ online
is that it forced us to think extensively about how a program to
generate the web site for an online journal would work.  Dave wrote a
lot of code, and we noted some things to be done better or differently
if another journal web site generation program was ever written.

\subsection{Contents, ordered by difficulty}
\label{sec:difficulty}

In early 2005 Dave and Karl began discussing the possibility of creating
an additional table of contents for each issue of \TUB\ that would be
organized by level of difficulty.  Karl took the issue to Barbara Beeton
and the other members of the \TUB\ production group, who supported the
idea.  \TUB\ Volume 25 (2005), No.~2 (\TUB\ issue 81) was the first
issue that included this additional table of contents: see
\url{http://tug.org/TUGboat/tb25-2/cover3.pdf}.  The design was
discussed extensively in advance, and has had only minor refinements
since that first appearance.

From the beginning, we knew we would want this information to be
available online (in \HTML) as well as in print (via \PDF).  So, we
devised a format for the source file that both could be compiled by
\TeX\ to produce \PDF, and would also be plausible to parse with a Perl
program to generate \HTML\ for the online contents page.  We informally
refer to these dual-purpose source files as ``capsule files''.

The capsule files begin with some prologue definitions relevant only to
\TeX, followed by the main material: a sequence of \verb|\capsule|
commands, each one a capsule summary of an item in the table of
contents.  The \verb|\capsule| entries are in the order they would
appear in the printed level-of-difficulty table of contents (since Perl
can do reordering more easily than \TeX).  The \verb|\capsule| command
evolved over time, eventually having nine arguments:

\begin{enumerate}
\item The difficulty rating\Dash follows \cs{capsule} on
     first line (example given below).
\item The \TUB\ category,
     possibly with a ``subargument'' \texttt{replace} or \texttt{add},
     as described below.  Arguments 2--7 are always alone on their lines.
\item The author(s).
\item The title.
\item A one-line description for the item.
\item The page number, possibly with an \texttt{offset} subargument.
\item The \URL\ of the item's \PDF.
\item Optional subtitles. These can be multiple lines.
\item Optional additional text for the \HTML.  This
      can also be multiple lines.
\end{enumerate}
(Some of the subtleties of the \verb|\capsule| command's interpretation
will be described in the next section.)

For ease of parsing by the Perl program, the arguments to
\verb|\capsule| are mostly on a single line (the exceptions are the last
two, which can be multiple lines, as noted above).  Here's an example
from the present issue:

{\small\hfuzz=6.6pt \begin{verbatim}
\capsule{Introductory}
  {Resources}
  {Jim Hef{}feron}
  {Which way to the forum?}
  {review of the major online help forums}
  {\getfirstpage{heff}}
  {/TUGboat/!TBIDENT!heff.pdf}
  {}
  {}
\end{verbatim}}


\section{Writing a program to generate \TUB~contents pages}

Even given the prior experience with \TPJ\ (described in
section~\ref{sec:tpj}), the program to generate the \TUB\ contents
pages and lists of authors, titles, and categories/keywords evolved over
a fairly long period.  As we handled more of \TUB's 100 issues, we
continually learned of more variations with which we had to cope.

\subsection{The series of steps}

Our memory of the evolution is as follows.

\LB{a}Dave first cobbled together a program to convert the capsule files
(which only existed from issue 81 on) into tables of contents for new
issues as they came out.  In this way, we began to understand the task
at hand and had real examples to review as we decided what to do next.

For this program, Dave reworked parts of the \textsl{Prac\TeX\ Journal}
program.  In particular, for this and all additional evolutions of the
project he used a pair of template routines he developed (originally to
generate \HTML\ for the \textsl{Prac\TeX\ Journal} effort), in order to
avoid learning about Perl's template capabilities; see
\url{http://walden-family.com/public/texland/perl-common-code.pdf}.

\LB{b}Then we started to process issues prior to \#81.  The material we
had to work with was (a)~the online contents pages, which existed as
hand-crafted \HTML\ (mentioned in section~\ref{sec:prior}); and
(b)~the so-called ``\texttt{.cnt} files'' created by Barbara Beeton;
these are \TeX\ files, covering (at the time) the tables of contents for
all but the last few years prior to issue 81.

(Aside: The \texttt{.cnt} files are also used by Nelson Beebe to produce
his \TUB\ bibliography files.  Both are available on \CTAN\ at
\url{http://mirror.ctan.org/info/digests/tugboat}.)

\LB{c}Where only \HTML\ files existed, Dave converted the \HTML\ into
capsule files using a combination of Perl programming, editor macros,
and manual editing.  At this point, the \URL{}s for the \PDF{}s of the
individual papers already existed in the \HTML\ for transfer to the
capsule files.  (When posting the scans, Karl had updated the \HTML\
contents files with these links to \PDF{}s for individual items.)

\LB{d} For the years which had a \texttt{.cnt} file available, Dave
wrote another Perl program for conversion into capsule files.  In this
case, Dave then looked at the \HTML\ files for those issues and
transferred the \URL{}s for the \PDF{}s into the capsule files.  Dave did
this manually, looking at each \PDF\ file as he went along, spotting
instances of multiple short or related papers in a single \PDF\ file
such that the same \URL\ would be the argument to more than one
\verb|\capsule| command.  (This happened because sometimes Karl had
combined several items into one \PDF, according to his subjective idea
of when splitting would be more hindrance than help to readers.)  In a
few instances, we split \PDF\ files that had previously been combined.

\LB{e}At this point, we had capsule files for all issues, and some
insight into the special cases that needed to be handled.  Dave then did
a major renovation and expansion of the main conversion program
(paragraph~a).  In addition to generating the tables of contents for
each issue, the new version of the program created author, title and
keyword lists across all issues.

\LB{f}Dave reran the new version of the program on the latest issues (see
paragraph~a) to make sure those capsule files still converted correctly.

\LB{g}Starting with the first issue, Dave then ran the new version of
the program on successive issues, fairly often discovering new
situations the program had to be augmented to handle and discussing
possible solutions with Karl.  Some of these situations and solutions
are described in the next sections.

\LB{h}Karl and Barbara reviewed the results and suggested additional
refinements.  Some of these just required fixes to the capsule files to
the program.  Others required changes to the program.

\LB{i}Finally, we felt ready to make the full set of computer-generated
web pages publicly available.  They are all linked from
\url{http://tug.org/TUGboat/contents.html}.

Over time, as new \TUB\ issues have been produced a little additional
program maintenance and improvement has been required.  Altogether there
have been about 50 iterations of the program.

\subsection{Program structure}

The program is driven by several plain text files:
\begin{itemize}

\item A file giving translations of words with diacritical marks,
etc., both from \TeX\ into \HTML\ for web site display and from \TeX\
into plain text for alphabetic sorting.

\item A file for unifying both (a)~different versions of the same author's
name, defining a single version of the name which is used for all when
sorting items for the author list), and (b)~different versions of the
same \TUB\ article category (e.g., `Fonts',
    `Font Forum',
    `Font Design and New Fonts', and
    `Fonts and Tools'), again defining a single version which is used
for the category/keyword list.

\item A file listing the \TUB\ issues to be processed in this run.

\item The capsule file for each issue.

\end{itemize}
Examples of all the files discussed here can be seen at
\url{http://tug.org/TUGboat/tb32-1/tubonline}.

The program reads the first two files to prime its data structures and
then begins processing the third file, one issue number at a time, which
in turn involves processing the capsule file for that issue.  As each
capsule file is processed, the necessary information is saved for the
title, author, and keyword\slash category lists.  The \HTML\ contents
page for each individual issue is also output in turn.  After all the
issues have been processed, the saved information for the three types of
lists is sorted appropriately, and the web pages for these lists are
created.

Thus, the program is not unusual: parsing, processing, output.  It is
inherently a bit messy because of different combinations of situations
that must be handled in different ways, for example, the different
combinations of the title, author, \TUB\ category, and \PDF\ \URL\ that
may be present, resulting in different output formats.

The web site generation program skips over the \TeX\ at the beginning of
the file until it reaches the first of the few \TeX\ commands it
understands, for instance, \verb|\issue{25}{2}{81}{2004}{}{}| which
indicates the year, volume number and issue number within the volume,
and overall issue sequence number, starting at 1 for the first issue of \TUB.

\subsection{Program capabilities}

Some of the capabilities of the program have already been mentioned,
such as its conversion of the \TeX\ with diacritical marks for a
person's name into \HTML\ with its equivalent diacritics for display on
the web pages, and also into the strictly English A--Z and a--z alphabet
for sorting.  Unifying different variations of author names and \TUB\
categories has also been previously mentioned.

The program must display slightly different table of contents pages for
proceedings than for non-proceedings issues. Additionally, twice (to
date) something that was not a normal \TUB\ issue was distributed by
\tug\ such that we nevertheless wanted to handle it as if it were a
\TUB\ issue: the preprints for the 2004 proceedings (which filled the
role of \TUB\ issue \#79), and the Euro\TeX\ 2005 proceedings (which
filled the role of \TUB\ issue \#85).  These instances require different
formatting.

Sometimes a capsule file has text to be included in the online table of
contents that doesn't appear in the printed edition (argument \#9 to
\cs{capsule}, see section~\ref{sec:difficulty}).  This is typically used
for links to videos of conference presentations and supplementary
information for an article.  Our program handles these commands by
simply passing along the \HTML\ to the output; the \TeX\ macros
for generating the printed cover ignore these commands.

We want the items in the online contents to be ordered according to
their appearance in the issue.  However, from issue 81 on, the items in
the capsule file are in the correct order for generating the
level-of-difficulty table of contents, so the program has to resort them
by page number.  The items in capsule files before issue 81 are
generally in page number order, but even then, sometimes the
start-of-article page numbers are insufficient.  Multiple items can
appear on the same page, some page numbers have a non-numeric format,
e.g., c3 for cover page 3 (the inside back cover), and other occasional
special cases.  Thus, an optional \verb|\offset{.1}|, (or \verb|{.2}|,
etc.), parameter may follow a page number in the page-number argument to
a \verb|\capsule| command, and these values are used to adjust the order
of things in the page-number sort.  \cs{offset} is ignored by \TeX.

Another feature eliminates a potential source of error.  In the example
at the end of section~\ref{sec:difficulty}, the page number is not given
directly: it's specified as \verb|\getfirstpage{heff}|.  Seeing that,
the program looks for an auxiliary file \url{heff/firstpage.tex}, as our
production directory is arranged.  \TeX\ itself creates that file
automatically when an issue is run, thus avoiding manually entering page
numbers.

The example shows one more small feature: the \URL\ is given as
\url{/TUGboat/!TBIDENT!heff.pdf} instead of
\url{/TUGboat/tb32-1/tb100heff.pdf}.  The curious directive
\verb|!TBIDENT!|\ came about after we had been creating capsule files
for new issues for some time.  We realized that (naturally enough) new
capsule entries were usually created by copying old ones, and it was
regrettably easy to neglect updating the issue number (\verb|32-1|), the
sequence number (\verb|100|), or both.  \verb|!TBIDENT!|\ simply expands
to that sequence; the actual values needed for the program to do the
expansion are given in the \cs{issue} command mentioned above.

We also added some consistency checking to the program for more help
in discovering typos, etc.:

\begin{itemize}
\item the \PDF\ files specified in the \URL{}s must actually exist (this
assumes the program is being run on \texttt{tug.org} itself with full
access to the archive of \PDF{}s of individual articles);

\item everything in the capsule file must end up in the output, i.e., 
no two items have identical page numbers (we manually differentiate with
\verb|\offset| when that would otherwise be the case).

\end{itemize}

\section{Opportunities}

Having the archives of \TUB\ available online made it possible for
people to access articles in old issues without having to find a
physical copy of the issue.  The attendant full lists of authors,
titles, and keywords are particularly useful to researchers (ourselves
included) trying to find things in the \TUB\ archive.  For example, we
have used those lists in doing background research for the \tug\
interview series
{\parfillskip=0pt\par\newpage\noindent}%
(\url{http://tug.org/interviews}), and in creating the
book \textsl{\TeX's 2\/\raise .9ex \hbox{\scriptsize 5} Anniversary},
which involved creating lists of papers from \TUB.  (A fuller
description of how that latter book came about is at
\url{http://tug.org/store/tug10/10paper.pdf}.)

From the outset of \TUB\ online, issues more than a year old were made
publicly available.  A year after the publication of each new issue, it
was posted to the \TUB\ web site.  Following this precedent, we
immediately put all older issues online in full as the material became
available.

Having so much more of \TUB\ available online brought home the question
of the extent to which non-members of \tug\ would have access.
Eventually, the \tug\ board of directors decided to put each issue
online for members to access as soon as the paper copy was published,
but to wait a year before making it available to non-members.  At about
the same time, members were offered a membership option (with a discount
from the regular cost of membership) where they were not sent paper
copies of \TUB\ and only accessed it online.  About 15 percent of
members choose this option.

In general it seems that having \TUB\ online is good for both \tug\
members and other people interested in \TeX, typography, and fonts.
Having \TUB\ online is consistent with \tug's mission:

\begin{quotation}\small
\noindent{}TUG is a not-for-profit organization by, for, and of its
members, representing the interests of TeX users worldwide and providing
an organization for people who are interested in typography and font
design.
\end{quotation}

%However, having \TUB\ available online to everyone has the downside
%concern of being one less (substantial) reason to join \tug.
%\Dash{}to subscribe to the journal.

\begin{comment}
Most recently, because the tables of contents for all \TUB\ issues
already existed in an readily parsable machine readable form, it was not
too difficult for TUG to make a deal with Mathematical Sciences
Publishers, http://mathscipub.org, led by Paolo Ney de Souza such that
they could include \TUB\ as part of their web site and sell subscriptions
to \TUB\ on behalf of itself and TUG.
\end{comment}

As for the specifics that we've presented here, having the machine
readable capsule files for all issues of \TUB\ allows easier reuse of
\TUB\ data in other, perhaps as yet unforeseen, contexts.

\medskip
\section*{Acknowledgments}

Barbara Beeton, Mimi Burbank, and Christina Thiele all searched their
memories and archives to help us.
{\hfuzz=.9pt\par}

As described in the beginning of the article, Mimi initiated the process
of getting \TUB\ issues online (among many other \TUB\ and \tug\ and
\TeX\ efforts).  We'd like to dedicate this article to her memory;
sadly, she passed away late last year (a full memorial appears elsewhere
in this issue).

\vskip1\baselineskip
\advance\signaturewidth by 3pt
\makesignature

\end{document}


\begin{comment}
FROM Mimi

The "production team" came into being in 1996 - because we were so far
behind.  The files were on the computers at FSU - and everyone on the
team had accounts on the machines there.  Barbara had always wanted to
make the files available, and since she had access to them on the FSU
computers, it was easy just to grab them and move them to their new
home.

The articles were run using pdfLaTeX - and PDF files were the final
output I believe.  The only real problems were those files that used
newly designed software - and we always had Sebastian around to install
things for us so that we were able to run things on the machines at FSU.
I believe that actual production of some of the articles was one of the
real problems that Barbara had at the AMS - which was where all the
previous issues were run.  At FSU, we had carte blanche to install
whatever we wanted, and we maintained the system for a whole bunch of
operating systems.

I believe I actually made the index from the final 'run'    - raw HTML...


But - you'll really need to get all of this confirmed by Barbara - she
was the 'boss' we were just the day-laborers...
\end{comment}
