% $Id$
% cover2.tex - inside front cover of TUGboat. Public domain.

\input tugboat.sty
\input ../tugboat.dates
\TUBfinal

\def\rateyear{\the\year}
%\def\rateyear{\count255=\year\advance\count255 by 1 \the\count255}
\def\tug{\acro{TUG}}
\def\rtitle{}

\def\USA{U\kern-.12em.\kern.04em S\kern-.06em.\kern.06em A\null.}

\head * \TeX\ Users Group *

\TUB\/ (\acro{ISSN} 0896-3207) is published by the\newline
\TUG{}. Web: |tug.org/TUGboat|.

\bigskip \noindent {\bf Individual memberships}

\noindent
\rateyear\ dues for individual members are as follows
(all rates will likely have a small increase next year):

\begingroup
\raggedstretch=.3\colwd
\raggedright
\hyphenpenalty=10000
\item{\bull} Trial rate for new~members:~\$30.
\item{\bull} Regular~members:~\$105.
\item{\bull} Special~rate:~\$75.
\unskip\endgraf
\endgroup       % end \raggedright
\noindent The special rate is available to students, seniors, and
citizens of countries with modest economies, as detailed on our web
site.
%Also, anyone joining or renewing before March~31 receives a
%\$20 discount:
%\item{\bull} Regular~members (early bird):~\$85.
%\item{\bull} Special~rate (early bird):~\$55.
Members may also choose to receive \TUB\ and other benefits
electronically, at a discount. All membership options are described at
{\tt tug.org/join}.

Membership in the \TUG\ is for the calendar year, and includes all issues
of \TUB\/ for the year in which membership begins or is renewed, as well
as software distributions and other benefits.
Individual membership carries with
it such rights and responsibilities as voting in \acro{TUG} elections.
All the details are on the \acro{TUG} web site.

\bigskip \noindent {\bf Journal subscriptions}

\noindent \TUB\/ subscriptions (non-voting) are available to libraries
and other organizations or individuals for whom 
memberships are either not appropriate or desired.
Subscriptions are delivered on a calendar year basis.
The subscription rate for
\rateyear\ is~\$115.

\setbox\TestBox=\hbox{Category B:\enspace 99}
\def\Category #1: #2 - #3; #4; #5. {\noindent \hangindent\normalparindent
        \hbox to\wd\TestBox{Category #1:\hfil#2} subscriptions\dash
        educational \$#3;\penalty-20 \ %
        non-educational \$#4; additional \$#5 each.}

\bigskip \noindent {\bf Institutional memberships}

\noindent Institutional membership is primarily a means of showing
continuing interest in and support for \TeX\ and \tug.  It also
provides a discounted membership rate, site-wide electronic
access, and other benefits.  For further information, see
|tug.org/instmem| or contact the \tug\ office.

\bigskip \noindent {\bf Trademarks}

\noindent
Many trademarked names appear in the pages of \TUB.  If there is any
question about whether a name is or is not a trademark, prudence dictates
that it should be treated as if it is.

\bigskip \noindent {\bf About the cover}

\noindent The Alhambra-inspired tessellation on the cover was created by
Laurence Finston. His article on pages
\thisissuepageref{finston-alhambra} describes the process,
using his program \GNU\ 3\acro{DLDF}.

% more space above this.
\vskip 0pt plus1filll \bigskip\bigskip\noindent
[printing date: November \the\year]

\smallskip
\noindent Printed in \USA{}
\newcol

\NoParIndent

\def\1{\ifhmode\/\fi$^\ast$}
% \dag is too large; try to force it to be smaller; use \fivesy if necessary
%\def\2{$^{\hbox{$\scriptstyle\char"79$}}$}
\def\2{\/$^{\hbox{\fivesy\char"79}}$}
\def\person#1{{\def\\{, \it}\raggedstretch=.3\colwd\raggedright
        \hyphenpenalty=10000 \exhyphenpenalty=10000
        \hangindent\normalparindent #1\endgraf }}


\head * Board of Directors *

\vskip-2pt
\person{Donald Knuth\\Ur~Wizard of \TeX-arcana\2}
% \1 on title of president, not name, since ex officio.
\person{Arthur Rosendahl\\President\1}% 
\person{Boris Veytsman\1\\Vice President}%
\person{Karl Berry\1\\Treasurer}%
\person{Klaus H\"oppner\1\\Secretary}%
\person{Barbara Beeton\1}% \\\TUB~Editor}%
\person{Johannes Braams}%
\person{Max Chernoff}%
\person{Kaja Christiansen}%
\person{Ulrike Fischer}%
\person{Jim Hef{}feron}%
\person{Tom Hejda}%
\person{J\'er\'emy Just}%
\person{Frank Mittelbach}%
\person{Ross Moore}%
\person{Norbert Preining}%
%\person{Raymond Goucher\\Founding Executive Director\2}
\person{Raymond Goucher (1937--2019)\\ 
  \null\kern5.15em Founding Executive Director}
\person{Hermann Zapf (1918--2015)\\Wizard of Fonts}

\smallskip
{\eightpoint\it\raggedright %
 \1member of executive committee\break
 \2honorary\endgraf}

\smallskip
{\ninepoint
See |tug.org/board| for a roster of all past and present
board members, and other official positions.
\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
{\ninepoint
\setbox\TestBox=\hbox{Portland, \acro{OR} 97208-2311}
\line{%
\vtop{\hsize=\wd\TestBox
\obeylines
{\bf Addresses}
\smallskip

%General correspondence,
%All correspondence,
%\leavevmode\qquad payments, parcels,
%\leavevmode\qquad etc.
%\leavevmode\qquad payments, etc.
\TeX\ Users Group
\POBox 2311
Portland, \acro{OR} 97208-2311
\USA{}

\medskip
{\bf Telephone}
+1 503 223-9994
%\vskip\baselineskip

\medskip
{\bf Fax}
+1 815 301-3568
%\vskip\baselineskip

\medskip
{\bf Web}
|tug.org|
|tug.org/TUGboat|

}\quad
\vtop{
\rightskip=0pt plus\hsize
\hyphenpenalty=10000
\NoBlackBoxes
\obeylines
{\bf Electronic mail}
\smallskip
General \rlap{correspondence,}
membership, \rlap{subscriptions:}
|office@tug.org|

\medskip
Submissions \rlap{to \TUB,}
letters to \rlap{the Editor:}
|TUGboat@tug.org|

\medskip
Volunteer \TeX{}nical support,
public mailing list:
|support@tug.org|

\medskip
Contact the
Board of \rlap{Directors:}
|board@tug.org|

}\hss}}

%\bigskip
%{\bf Have a suggestion? Problems not resolved?}\newline
%The \acro{TUG} Board wants to hear from you:\newline
%Please email |board@tug.org|.

\vskip 0pt plus1filll %\bigskip\bigskip

{\eightpoint
\parindent=0pt \parskip=4pt \raggedright
Copyright \copyright{} \the\year\ \TUG{}.

Copyright to individual articles within this publication remains with
their authors, so the articles may not be reproduced, distributed or
translated without the authors'~permission.

For the editorial and other material not ascribed to a particular
author, permission is granted to make and distribute verbatim copies
without royalty, in any medium, provided the copyright notice and this
permission notice are~preserved.
  
Permission is also granted to make, copy and distribute translations
of such editorial material into another language, except that the \TUG{}
must approve translations of this permission notice itself.  Lacking
such approval, the original English permission notice must be~included.
An information notice to the \TUB\ editors regarding such redistribution
is appreciated.

%% copyright notice replaced 26 June 2003; text provided by Karl Berry
%% final sentence added 3 July 2022 by Barbara Beeton
}
\vfilneg
\end
